Efficiency

### 2018-05-21 DraftExec.tex
with ross acknowledged :-)
bump

\usepackage{draftwatermark}
\SetWatermarkText{DRAFT}
\SetWatermarkScale{1.5}
\SetWatermarkLightness{0.95}

\title{Efficiency}
\author{Aidan Morrison}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

\begin{titlepage}
    \begin{center}
        \vspace*{1cm}

        \vspace{10cm}
        \textbf{\huge A comparison of pumpjets and propellers for non-nuclear submarine propulsion}

        \vspace{0.5cm}

        \vspace{1.5cm}

        \textbf{Aidan Morrison}

        \vspace{1.5cm}
        January 2018

        \vfill

    \end{center}
\end{titlepage}

@@

The development of this line of inquiry into of the full substance of this paper has come about not due to my own intrigue, but largely due to the determination and interest of Gary Johnson.  Through mutual networks in industry and academia we discovered that we had both been intrigued by the technology choice, and considered it of potential significance to Australia's national interest. Australia is fortunate to have citizens so concerned with national interest to so substantially invest in research to advance public debate.  Unless he had commissioned me to write it, there is no way that I would have been able to make the sustained and deliberate inquiry which the topic required to reach a useful level of quantification and confidence to meaningfully inform debate.

>>>>

% for cover page
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{graphicx}

% \usepackage{draftwatermark}
% \SetWatermarkText{DRAFT}
% \SetWatermarkScale{1.5}
% \SetWatermarkLightness{0.95}

\title{Efficiency}
\author{Aidan Morrison}

% \SweaveOpts{concordance=TRUE}
\definecolor{titlepagecolor}{cmyk}{0, 0, 0, .30}
\definecolor{namecolor}{cmyk}{0, 0, 0, .80}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

%-----------------------------------------------------------------

% ----------------------------------------------------------------
\begin{titlepage}
\newgeometry{left=7.5cm} %defines the geometry for the titlepage
\pagecolor{titlepagecolor}
\noindent

{\huge \textsf{A comparison of pumpjets and}}
\vskip\baselineskip
{\huge \textsf{propellers for non-nuclear}}
\vskip\baselineskip
{\huge \textsf{submarine propulsion}}
\vskip\baselineskip
\noindent
\textbf{Aidan Morrison}
\vskip\baselineskip
\textsf{January 2018}
\vskip\baselineskip
\vskip\baselineskip

\vfill
\noindent

\includegraphics[width=6cm]{tl_logo.png}\\[-1em]
\color{white}
\makebox[0pt][l]{\rule{1.3\textwidth}{1pt}}
\par
\noindent
\textbf{\textsf{Trendlock}} \textcolor{namecolor}{\textsf{Consulting}}

\end{titlepage}
\restoregeometry % restores the geometry
\nopagecolor% Use this to restore the color pages to white

@@

The development of this line of inquiry into of the full substance of this paper has come about not due to my own intrigue, but largely due to the determination and interest of Gary Johnson.  Through mutual networks in industry and academia we discovered that we had both been intrigued by the technology choice, and considered it of potential significance to Australia's national interest. Australia is fortunate to have citizens so concerned with national interest to so substantially invest in research to advance public debate.  Unless he had commissioned me to write it, there is no way that I would have been able to make the sustained and deliberate inquiry which the topic required to reach a useful level of quantification and confidence to meaningfully inform debate.  In addition, the support of my colleague from Trendlock, Ross Ireland, was invaluable in producing the extensive modelling required.
